% !TEX program = xelatex
\documentclass[11pt]{resume}

\geometry{
    left=1.5cm,
    right=9cm,
    marginparwidth=7cm,
    marginparsep=0.5cm,
    top=1.5cm,
    bottom=1.5cm,
    footskip=2\baselineskip
}

\begin{document}

    \name{Tommy White}
    \contactbar{
        \email{tw@tommy-w.com}
        \phone{(555) 012-3456}
        \location{Town, ST}
        \github{websurfin}{https://github.com/websurfin}
        \website{tommy-w.com/}
    }

    \begin{fullwidth}
    \makecontactbar
    \end{fullwidth}
    
    \sffamily


    %% EXPERIENCE SECTION
    \resumesection[sidebar]{Experience}
    
    \datedentry
        {Research Assistant}
        {Dartmouth College/Dartmouth Security and AI Lab}
        {Sept 2018 -- March 2021}
        {Hanover, NH}
    
    \begin{itemize}
        \setlength{\itemindent}{-0.8em}
        \item Developed and formalized novel algorithms in the fields of 
            \href{http://eliassi.org/papers/ai-mag-tr08.pdf}{Collective Classification} and 
            \href{https://arxiv.org/ftp/arxiv/papers/1812/1812.08434.pdf}{Graph Neural Networks}.
        \item Applied these algorithms to \href
            {https://en.wikipedia.org/wiki/Link_prediction#Problem_definition}
            {Social Network prediction problems}.
        \item Managed datasets with terabytes of data as well as the dozens of computation jobs used to
            process and analyze this data.
    \end{itemize}

    \divider
        
    % \datedentry
    %     {Teaching Assistant}
    %     {Dartmouth College}
    %     {Nov. 2020 -- March 2021}
    %     {Hanover, NH}
    
    % \begin{itemize}
    % \setlength{\itemindent}{-0.8em}
    %     \item Produced and graded educational materials for a class on the Foundations of Applied 
    %         Computing.
    %     \item Hosted office hours and TA lessons virtually without issue.
    % \end{itemize}
    % \divider

    \datedentry
        {Software Engineering Internship}
        {Amazon.com}
        {Jan. 2017 -- Dec. 2017}
        {San Luis Obispo, CA}

    \begin{itemize}
        \setlength{\itemindent}{-0.8em}
        \item Worked as part of an Amazon Prime server team; my code has directly affected millions of
            transactions.
        \item Redeveloped the code deployment pipeline and rollback system to enable my team to 
            quickly recover from issues in production code.
        \item Developed API to facilitate automatic upselling of Prime memberships to customers 
            based on their current membership status, region, and other factors.
    \end{itemize}

    \medskip

    %% PROJECTS SECTION
    \resumesection{Projects}
    \datedentry
        {Social Network Analysis for Cryptocurrency Price Prediction}
        {Dartmouth Security and AI Lab}
        {Feb. 2019 -- March 2021}
        {}
    
    \begin{itemize}
        \setlength{\itemindent}{-0.8em}
        \item Developed algorithms to predict future prices of top cryptocurrencies by analyzing massive amounts of
            social media data.
        \item Organized and monitored tens of thousands of hours of computation time to complete 
            the experiments.
        \item Presented results at \href{https://www.computer.org/csdl/proceedings/blockchain/2019/1gjS4tubCmI}
            {2019 IEEE International Conference on Blockchain and Cryptocurrencies} in Atlanta, GA.
    \end{itemize}

    \divider

    \datedentry
        {Counter-terrorism Graph Time Series Analysis}
        {Dartmouth Security and AI Lab}
        {Oct. 2018 -- March 2021}
        {}

    \begin{itemize}
        \setlength{\itemindent}{-0.8em}
        \item Explored prediction problems in a social network styled dataset which included thousands of terrorists and hundreds of 
            terroristic factions as members.
        \item Improved predictive performance by generating novel features based on centrality, flow, and balance metrics.
            \item Primarily usied centrality metrics across monthly subnetworks of terrorist factions.
    \end{itemize}

    \divider

    \large\bfseries See more of my experience/projects at \href{https://tommy-w.com/}{tommy-w.com/}

\end{document}
