% !TEX program = xelatex
\documentclass[11pt]{resume}

\geometry{
    left=1.5cm,
    right=9cm,
    marginparwidth=7cm,
    marginparsep=0.5cm,
    top=1.5cm,
    bottom=1.5cm,
    footskip=2\baselineskip
}

\begin{document}

    % PLACE NAME FIRST TO HAVE AT TOP
    \name{Tommy White}
    \personalinfo{
        \email{<address>@<website>}
        \phone{(555) 012-3456}
        \location{<address or city>}
        \github{websurfin}{https://github.com/websurfin}
        % \website{https://tommy-w.com/}
    }

    \begin{fullwidth}
    \makeheader
    \end{fullwidth}
    
    \sffamily

    % \resumesection[sidebar]{Purpose} % Customize this when applying to specific companies
    % To earn some money while tackling challenging problems related to machine learning, data 
    % science/management, cybersecurity, or general software development.

    %% EXPERIENCE SECTION
    \resumesection[sidebar]{Experience}
    
    \datedentry
        {Research Assistant}
        {Dartmouth College/Dartmouth Security and AI Lab}
        {Sept 2018 -- March 2021}
        {Hanover, NH}
    
    \begin{itemize}
        \item Developed and formalized novel algorithms in the fields of 
            \href{http://eliassi.org/papers/ai-mag-tr08.pdf}{Collective Classification} and 
            \href{https://arxiv.org/ftp/arxiv/papers/1812/1812.08434.pdf}{Graph Neural Networks}.
        \item Applied these algorithms to \href
            {https://en.wikipedia.org/wiki/Link_prediction#Problem_definition}
            {Social Network prediction problems}.
        \item Managed datasets with terabytes worth of data as well as the 
            \href{https://rc.dartmouth.edu/index.php/discovery-overview/}{computation jobs} used to
            process and analyze this data.
    \end{itemize}

    \divider
        
    % \datedentry
    %     {Teaching Assistant}
    %     {Dartmouth College}
    %     {Nov. 2020 -- March 2021}
    %     {Hanover, NH}
    
    % \begin{itemize}
    %     \item Produced and graded educational materials for a class on the Foundations of Applied 
    %         Computing.
    %     \item Hosted office hours and TA lessons virtually without issue.
    % \end{itemize}
    % \divider

    \datedentry{Software Engineering Internship}{Amazon.com}{Jan. 2017 -- Dec. 2017}{San Luis Obispo, CA}
    \begin{itemize}
        \item Worked as part of a Prime server team; my code has directly affected millions of
            transactions.
        \item Redeveloped our code deployment pipeline and rollback system to enable my team to 
            quickly recover from issues in production code.
        \item Developed API to facilitate automatic upselling of Prime memberships to customers 
            based on their current membership status, region, and other factors.
    \end{itemize}

    \medskip

    %% PROJECTS SECTION
    \resumesection{Projects}
    \datedentry
        {Social Network Analysis for Cryptocurrency Price Prediction}
        {Dartmouth Security and AI Lab}
        {Feb. 2019 -- March 2021}
        {}
    
    \begin{itemize}
        \item Developed algorithms to score social media users based on the relationship between 
            analysis of social media interaction graphs and price fluctuations of various 
            cryptocurrencies.
        \item Organized and monitored tens of thousands of hours of computation time to complete 
            the experiments.
        \item Presented results at 2019 IEEE Blockchain Conference in Atlanta, GA. Journal paper is
            a work in progress. 
    \end{itemize}

    \divider

    \datedentry
        {Counter-terrorism Graph Time Series Analysis}
        {Dartmouth Security and AI Lab}
        {Oct. 2018 -- March 2021}
        {}

    \begin{itemize}
        \item Explored prediction problems in a social network styled dataset which included thousands of terrorists and hundreds of 
            terroristic factions as members.
        \item Improved predictive performance by generating novel features based on centrality, flow, and balance metrics.
            \item Primarily using centrality metrics across monthly subnetworks of terrorist factions.
    \end{itemize}


\end{document}
